%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Revision author (current version):
% Sangeeta Menon (https://sangeetamenon.github.io/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{SANGEETA MENON} % Your name
\address{\bf Information Developer | Technical Writer} % Your profession
\address{\bf (+91)9945313249 \\ sangeeta.tw@gmail.com \\ sangeetamenon.github.io} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL SUMMARY SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Summary}
{\bf Technical Writer} with more than {\bf 16 years of experience} in developing and managing technical information for engineering and software products, while working in various domains such as {\bf Telecommunications}, {\bf Networking}, and {\bf Health Care}. Prior to that, I worked for more than 4 years in creating non-technical content for healthcare and shopping portals.
\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technical Skills & Basic understanding of programming in C/C++, Java, and Python\\
Markup Languages & HTML, XML, Markdown (with Git and GitHub) \\
Authoring Tools & Confluence Wiki, MS Word, Robohelp 8, Adobe Framemaker 10 \\
Image Editing Tools & Adobe Photoshop, Hypersnap, Snag IT, Microsoft Visio, Camtasia studio \\
Defect Tracking Tool & JIRA, ClearQuest \\ 
Content Management & Documentum, VSS \\ 
Style Guide & Microsoft Style Guide \\ 
Soft Skills & SMEs Interviews, Multi-tasking, Problem Solving, Continuous Learning
\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Ribbon Communications}{February 2014 - May 2020}{Principal Technical Writer}{6 years 3 months}
\item {\bf Products:} Session Border Controller (SBC), Signaling Gateway (SGX), DataStream Integrator (Server and Cloud).
\item Interviewed SMEs, researched, and developed high-quality documents such as Installation and Configuration guide, Upgrade guide, Feature guide, Alarms and Traps guide, REST API User guide, and Command‐line Interface (CLI) guide.
\item Iterated and improved documents based on stakeholder feedback, using JIRA for issue tracking and resolution reports.
\item Created project plans, resource and effort estimates, reports for tracking project status and progress, team performance metrics.
\item Proactively identified risks and bottlenecks in workflow and publishing process.
\item Strategized, innovated, and implemented solutions to improve operational efficiency.
\item Contributed to editorial reviews, document aesthetics, style guide, internal knowledge base.
\item Developed training materials for new employees.
\item Mentored junior writers to improve their knowledge and productivity.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{IP Infusion Pvt. Ltd.}{January 2013 - February 2014}{Senior Technical Writer}{1 year 2 months}
\item {\bf Products:} ZEBOS Network Platform, Aeroz Network Platform.
\item Planned and developed User guide, Installation guide, Configuration guide, API guide, and CLI guide.
\item Managed SME feedback, ensured document correctness and completeness.
\item Tested documents for clarity, readability, and user experience.
\item Created standardized templates, style guide, checklist, standards, guidelines, and procedures.
\item Assisted the Lead Quality Consultant in various QMS tasks for CMMi reassessments.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{OnMobile Global Ltd.}{March 2010 - December 2012}{Technical Writer}{2 years 9 months}
\item {\bf Products:} Mobile, Messaging, and Marketing unit (M3PU).
\item Planned, authored, reviewed, and improved Getting Started guide, Architecture guide, Training guide, User guide, Product Notes, Installation guide, API guide, Proposal documents, Product Brochures, Technical Support documents, and Release Notes.
\item Tested product GUIs for usability and user experience, .
\item Created aesthetically pleasing system diagrams for Software Architects.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Dynpro (for IBM)}{July 2008 - January 2010}{Technical Writer}{1 year 7 months}
\item {\bf Products:} Nokia Siemens Network - 4G.
\item Researched and developed User guide, Interface guide, Statistics guide, Command Line Interface (CLI) guide
\item Improved documents based on feedback from engineers, product managers, and customers.
\item Tested documents in development environments.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{ArisGlobal Software Networks}{December 2005 - March 2008}{ Senior Technical Writer}{2 years 3 months}
\item {\bf Products:} Arisg, Agxchange, CTM, Communications.
\item Authored User guide, Admin guide, Installation guide, Database guide, and Online Help, while ensuring strict compliance with user documentation process.
\item Reviewed and formatted Functional Specification Documents (FSDs), Release Notes, Standardized Documentation Templates.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Other Experiences}{}{}{}
\item Clinical Data Manager (\emph {May 2003 - January 2005}) at Pfizer India Ltd.
\item Catalogue Manager at e-officeplanet.com. 
\item Content Specialist at Cyberspace Infosys Solutions.
\item Content Designer at Aptech Ltd.
\item Quality Assurance Professional at Raptokos Brett Co. Ltd.
\item Trainee Quality Assurance at Parke-Davis Ltd.
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Recognition}

\begin{rSubsection}{Ribbon Communications}{}{}{}
\item Accorded the title of “Role Model” during Performance Appraisal 2018.
\item Nominated for Individual Excellence award for initiating quality in documentation.
\item Received Spot award, Easy Button award.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{OnMobile Global Ltd}{}{}{}
\item Received a ‘Pat-in-back’ award for achieving excellence in documentation.
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{rSubsection}{Advanced Diploma
in Software Engineering Technology}{}{Asset International}{}
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{M.Sc Chemistry}{}{Institute of Science}{}
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
